Example and Tutorial for Vim Editor (Linux)

### 2019-12-30 nontex/install/linux/fn_vim.Rmd
vim windows set-up complete

" For Goyo
let g:goyo_width=85

@@

" Color theme plugins
Plug 'joshdick/onedark.vim'
Plug 'morhetz/gruvbox'
Plug 'junegunn/seoul256.vim'
Plug 'jaredgorski/spacecamp'
Plug 'lifepillar/vim-solarized8'

@@

"""""""""""""""""""""""""""""""""""""""""""""""""
" Color Settings
"""""""""""""""""""""""""""""""""""""""""""""""""

syntax on

@@

" vim-solarized8:
" set background=dark
" colorscheme solarized8
```

>>>>

"""""""""""""""""""""""""""""""""""""""""""""""""
" Visual Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" For Goyo
let g:goyo_width=85

@@

" Markdown
Plug 'godlygeek/tabular'
Plug 'plasticboy/vim-markdown'

" Visual Settings
Plug 'junegunn/goyo.vim'
Plug 'junegunn/limelight.vim'
Plug 'reedes/vim-pencil'

" Color theme plugins
Plug 'joshdick/onedark.vim'
Plug 'morhetz/gruvbox'
Plug 'junegunn/seoul256.vim'
Plug 'jaredgorski/spacecamp'
Plug 'lifepillar/vim-solarized8'
Plug 'reedes/vim-colors-pencil'

@@

@@

" vim-solarized8:
" set background=dark
" colorscheme solarized8

" vim-colors-pencil:
" let g:pencil_higher_contrast_ui = 0
" colorscheme pencil
" set background=dark

"""""""""""""""""""""""""""""""""""""""""""""""""
" Visual Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" For Goyo
let g:goyo_width=85

" For LimeLight
" Color name (:help cterm-colors) or ANSI code
let g:limelight_conceal_ctermfg = 'gray'
let g:limelight_conceal_ctermfg = 240
" Color name (:help gui-colors) or RGB color
let g:limelight_conceal_guifg = 'DarkGray'
let g:limelight_conceal_guifg = '#777777'
" if Limelight should highlight line rather than paragraph
" let g:limelight_bop = '^.*$'
" let g:limelight_eop = '\n'
let g:limelight_paragraph_span = 0

"""""""""""""""""""""""""""""""""""""""""""""""""
" UI Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" Keep cursor in the middle of the page, useful for editing text
set so=999
" Turn limelight on by default
" autocmd VimEnter * Limelight
" Turn Goyo on by default
autocmd VimEnter * Goyo

"""""""""""""""""""""""""""""""""""""""""""""""""
" Markdown **, * etc settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" set concealcursor=n
" set conceallevel=3
" hi Asterisks NONE
" hi AsteriskBold  cterm=bold gui=bold
" syn match Asterisks contained "**" conceal
" syn match AsteriskBold "\\\@<!\*\*[^"*|]\+\*\*" contains=Asterisks
autocmd VimEnter * highlight Normal ctermbg=black
" ctermfg=grey

"""""""""""""""""""""""""""""""""""""""""""""""""
" Other Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
set paste               " to enable pasting in windows
```

```
nvim "C:/Users/d674a/Tex4Econ/_other/equation/multilines.tex"
```
